Sketch Recognition and Understanding

### 2009-08-15 trunk/draft/System.tex
after finished cite of svm

@@

Let us consider  a two class classification task with datapoints $x_i$ where $i=1,\cdots,m$ having corresponding labels $y_i=\pm1$ where if  $y_i=1$ if $x_i$ belonged to first class and $y_i=-1$ if $x_i$ belonged to second class. Each data  point $x_i$ is represented in $N$ dimensional input or attribule space. Let the classification plane be represented as function . 
\begin{equation}
 y=f(x)=sign(\omega \cdot x - b)
\label{eq:planeEq}
\end{equation}

@@

The SVM problem is how to construct the plane that is furthuest from both classes. One approcah is to maximize the margin between two parallel planes supporting. A plane supports a class if all points in that class are on one side of that plane. For the points with the class label $+1$ we would like there exist $\omega$ and $b$ such that $\omega \cdot x_i\> b$ or $\omega \cdot x_i -b \> 0$  depending on the class label. Let us suppose that smallest value of $\mid \omega \cdot x_i -b\mid$ iss $\kappa$, then when $ \omega \cdot x_i -b \geq \kappa$. The argument insidee the decision function is invariant under positive rescalling so we will implicity fix a scale by requiring $\omega \cdot x_i -b \geq 1 $. For the points with class label $-1$ we similary require $\omega \cdot x_i -b \leq -1 $. To find the plane furthest from both setss, we can simply maximize the distance or margin between the support planes for each class as illustrated in Figure \ref{fig:svm2}. The support planes are pussshed apart untill they bump inot small number of data points ( the support vecotrs ) for each class. The support vectors in Figure \ref{fig:svm2} are filled datapoints , 
\begin{figure}
	\centering
		\includegraphics{afterDefense/svm2.jpg.eps}
	\caption{Margin of Support planes }
	\label{fig:svm2}
\end{figure}

@@

\subsubsection{Linearly Inseperable Case}
 So far we have assumed that the two datasets are linearly separable. Th this is not true, the startegy of constructing the plane that bisect the two closest points of the convex hulls will fail. As illustrated in Figure \ref{fig:svm5}, if the points are not linearly seperable the primal supporitng plane will fails. Since the QP task is not feasible for ethe linearly inseperable case , then we need to relax the constrains. Consider the linear inseperable problem in Figure\ref{fig:svm5}, Ideally we would like no points to be missclassified and no points to fall in the margin. But we must relax the constrain that insure that each point in on the approiate side of tis supporitng plane. Any point fallihng on the wrong side of tis supprting plane is considered to be an error. We want to maximize the margin and minimize the error.

@@

\begin{equation}
\begin{array}{c}
\min_{\alpha} \ \ \   \frac{1}{2} \sum_{i=1}^{m}{\sum_{j=1}^{m}{y_iy_j\alpha_i\alpha_j\vartheta(x_i)\vartheta(x_j)}} - \sum_{i=1}^{m}{\alpha_i} \\
s.t. \ \ \sum_{i=1}^{m}{y_i\alpha_i}=0   \\
 C \geq \alpha_i \geq 0  \ \ \ i=1,\cdots , m 
 \end{array} 
\label{eq:dualkernel}
\end{equation}
Notice that the mapped data only occurs as inner product in the objective. Now we apply a little mathematically rigorous magie known as hilbern schmidt kernels, first applied to SVMs in \cite{}.  By Mercer's theorem, we knoew that for ccertain mapping $\theta$ and any two points $u$ and $v$, the inner product of the the mapped points can be evalutated using the kernel function without ever explicity knowing ht emapping , e.g., $\theta(u)\theta(v)\equiv K(u,v)$. Some of the more popular known kernels are given below. New kernel are being developed to fit domian specific requriments. 
\begin{center}
	\begin{tabular}{cc}
	$\vartheta(u)$  & $K(u,v)$ \\ \hline 
	Degree $d$ polynomial & $\left(u\cdot v +1\right)^d$ \\ 
	Radial Basis Function & $\exp \left( - \frac{\left\|u-v\right\|^2}{2\sigma}\right) $ \\ 
		Two layer Neural Network& $ sigmoid \left(\eta\left(u\cdot v +1\right)+c\right)$ \\

@@

\subsubsection{ SVM in Machine Learning }
SVM has been successfully applied to a number of applications ranging from particle identification \cite{}. Face detection  \cite{} and text categorization \cite{} to engine knock detection. SVMs are very suited to the classification task that commonly arise in machine vision. As an example we consider and application involving face identification\cite{}.  Three different SVM classiifer were used on training set of 200 images (5 image per person). The error rate was less than 5\%. An RBF network and SVM classifiers were compared on the UPUS handwritten digit recognition database\cite{}.  SVM outperformed and RBF network on all digits.

@@

SVM have been applied ot the a largest MNIST a Handwritten digit recognition dataset of 60000 training set and 10000 test set\cite{}. Sherif and Ezzat has performed a comparision between SVM and several other techniques on the MNIST dataset. They also compared the same classfication methods on arabic handwritten digits (MADBASE) \cite{}. Their results shows that SVM classifier outperform all other techniques on both MNIST and MADBase datasets and achieved recognition rate of over 98\%. Similar results was reported by \cite{} on the MNIST dataset. Ther are many other successful application SVM. They have proven to be robust to noise and perform well on many tasks.

@@

For the first category the most obvioius  approach is to sequentially update the $\alpha_i$  and this is the approach used by the kernel  Adtron (KA) algorithm \cite{}.

Chunking and decomposition methods optimize the SVM with respect to subsets. Rather than sequentially updateing the $\alpha_i$ the alternative is to upodate the $\alpha_i$ in parallel but using only a subset or wokring set of data at each stage. There are many successful code based on these decomposition strategies. SVM codes available online such as SVMTorch \cite{} and SVMLight \cite{} use these working set strategies.

The third approach is to directly attack the SVM  problem from and optimization prespective and create algorithms that explicity exploits the structure of teh problem. Keerthi et al. \cite{} proposed a very effective algorithm based on the dual geometry of finding the two closest points in the convex hulls.

>>>>

\subsection {Trainig the SVM}
\subsection {Testing}

@@

Let us consider  a two class classification task with datapoints $x_i$ where $i=1,\cdots,m$ having corresponding labels $y_i=\pm1$ where if  $y_i=1$ if $x_i$ belonged to first class and $y_i=-1$ if $x_i$ belonged to second class. Each data  point $x_i$ is represented in $N$ dimensional input or attribule space. Let the classification plane be represented as function. 
\begin{equation}
 y=f(x)=sign(\omega \cdot x - b)
\label{eq:planeEq}
\end{equation}

@@

The SVM problem is how to construct the plane that is furthuest from both classes. One approcah is to maximize the margin between two parallel planes supporting. A plane supports a class if all points in that class are on one side of that plane. For the points with the class label $+1$ we would like there exist $\omega$ and $b$ such that $\omega \cdot x_i\> b$ or $\omega \cdot x_i -b \> 0$  depending on the class label. Let us suppose that smallest value of $\mid \omega \cdot x_i -b\mid$ iss $\kappa$, then when $ \omega \cdot x_i -b \geq \kappa$. The argument inside the decision function is invariant under positive rescalling so we will implicity fix a scale by requiring $\omega \cdot x_i -b \geq 1 $. For the points with class label $-1$ we similary require $\omega \cdot x_i -b \leq -1 $. To find the plane furthest from both setss, we can simply maximize the distance or margin between the support planes for each class as illustrated in Figure \ref{fig:svm2}. The support planes are pussshed apart untill they bump inot small number of data points ( the support vecotrs ) for each class. The support vectors in Figure \ref{fig:svm2} are filled datapoints , 
\begin{figure}
	\centering
		\includegraphics{afterDefense/svm2.jpg.eps}
	\caption{Margin of Support planes }
	\label{fig:svm2}
\end{figure}

@@

\subsubsection{Linearly Inseperable Case}
 So far we have assumed that the two datasets are linearly separable. This is not true, the startegy of constructing the plane that bisect the two closest points of the convex hulls will fail. As illustrated in Figure \ref{fig:svm5}, if the points are not linearly seperable the primal supporitng plane will fails. Since the QP task is not feasible for ethe linearly inseperable case , then we need to relax the constrains. Consider the linear inseperable problem in Figure\ref{fig:svm5}, Ideally we would like no points to be missclassified and no points to fall in the margin. But we must relax the constrain that insure that each point in on the approiate side of tis supporitng plane. Any point fallihng on the wrong side of tis supprting plane is considered to be an error. We want to maximize the margin and minimize the error.

@@

\begin{equation}
\begin{array}{c}
\min_{\alpha} \ \ \   \frac{1}{2} \sum_{i=1}^{m}{\sum_{j=1}^{m}{y_iy_j\alpha_i\alpha_j\vartheta(x_i)\vartheta(x_j)}} - \sum_{i=1}^{m}{\alpha_i} \\
s.t. \ \ \sum_{i=1}^{m}{y_i\alpha_i}=0   \\
 C \geq \alpha_i \geq 0  \ \ \ i=1,\cdots , m 
 \end{array} 
\label{eq:dualkernel}
\end{equation}
Notice that the mapped data only occurs as inner product in the objective. Now we apply a little mathematically rigorous magie known as hilbern schmidt kernels, first applied to SVMs in \cite{svmintroduce}.  By Mercer's theorem, we knoew that for ccertain mapping $\theta$ and any two points $u$ and $v$, the inner product of the the mapped points can be evalutated using the kernel function without ever explicity knowing ht emapping , e.g., $\theta(u)\theta(v)\equiv K(u,v)$. Some of the more popular known kernels are given below. New kernel are being developed to fit domian specific requriments. 
\begin{center}
	\begin{tabular}{cc}
	$\vartheta(u)$  & $K(u,v)$ \\ \hline 
	Degree $d$ polynomial & $\left(u\cdot v +1\right)^d$ \\ 
	Radial Basis Function & $\exp \left( - \frac{\left\|u-v\right\|^2}{2\sigma}\right) $ \\ 
		Two layer Neural Network& $ sigmoid \left(\eta\left(u\cdot v +1\right)+c\right)$ \\

@@

\subsubsection{ SVM in Machine Learning }
SVM has been successfully applied to a number of applications ranging from particle identification \cite{ParticleSVM7}. Face detection  \cite{faceSVM8,faceSVM7} and text categorization \cite{TextSVM7} to engine knock detection. SVMs are very suited to the classification task that commonly arise in machine vision. As an example we consider and application involving face identification\cite{faceSVM8}.  Three different SVM classiifer were used on training set of 200 images (5 image per person). The error rate was less than 5\%. An RBF network and SVM classifiers were compared on the UPUS handwritten digit recognition database\cite{ORLDataset}.  SVM outperformed and RBF network on all digits.

@@

SVM have been applied ot the a largest MNIST a Handwritten digit recognition dataset of 60000 training set and 10000 test set\cite{IjdarSherifPaper}. Sherif and Ezzat has performed a comparision between SVM and several other techniques on the MNIST dataset. They also compared the same classfication methods on arabic handwritten digits (MADBASE) \cite{ADBase9,IjdarSherifPaper}. Their results shows that SVM classifier outperform all other techniques on both MNIST and MADBase datasets and achieved recognition rate of over 98\%. Similar results was reported by \cite{empiricalcomp11,SVMInvariantComDecoste02} on the MNIST dataset. Ther are many other successful application SVM. They have proven to be robust to noise and perform well on many tasks \cite{empiricalcomp11,Scholkopf97comparingsupport}.

@@

For the first category the most obvioius  approach is to sequentially update the $\alpha_i$  and this is the approach used by the kernel  Adtron (KA) algorithm \cite{kernelSVM4}.

Chunking and decomposition methods optimize the SVM with respect to subsets. Rather than sequentially updateing the $\alpha_i$ the alternative is to upodate the $\alpha_i$ in parallel but using only a subset or wokring set of data at each stage. There are many successful code based on these decomposition strategies. SVM codes available online such as SVMTorch \cite{svmTorch} and SVMLight \cite{SVMlight} use these working set strategies.

The third approach is to directly attack the SVM  problem from and optimization prespective and create algorithms that explicity exploits the structure of teh problem. Keerthi et al. \cite{fastSVM6} proposed a very effective algorithm based on the dual geometry of finding the two closest points in the convex hulls.
